---
title: "lj_investigate"
author: "wangsy"
date: "2025-09-15"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
header-includes:
  - \usepackage{ctex}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## One:Main Conclusions

This chart is extracted from the Lianjia database, showing the distribution of a scatter plot between the age of properties and their floor area. 80% of the houses are from the last 30 years, with a small portion exceeding 50 years in age. 95% of the properties have an area of less than 200 square meters, with the majority being under 100 square meters. For more details on using data analysis see <https://github.com/tigerwangcqupt/r_projects-static_project_01.git>.

## Two:Analysis of ideas and method

```{r data define}
library(tidyverse)
library(dplyr)
library(conflicted)
library(showtext)
font_add("SimSun", "simsun.ttc")  # 添加系统字体
showtext_auto()  # 自动启用字体
conflicts_prefer(dplyr::filter)
conflicts_prefer(dplyr::lag)
load("../data/lj_sh_2019.RData")
```

Specific chart display:

```{r data plot, echo=FALSE}
lj %>%
  mutate(building_age=(2025-building_year)) %>%
  ggplot() +
  geom_point(aes(building_age,building_area))
```

## Three:Analysis Process

| 房子年代 | 建筑面积 | 占比 |
|----------|:--------:|-----:|
| 10       |   100    |  80% |
| 20       |    80    |  70% |
| 30       |    90    |  60% |

Based on the provided data and R data modeling, the following report data is generated.
